### 2011-01-26 paper/learningMethods.tex
Wrap
Reworked a bit of learningMethods

For both of these reasons, an intelligent learning algorithm is
needed.

In this context, by learning algorithm we mean a method for choosing:

\begin{enumerate}
\item The value for $\vec{\theta}$ for the initial trial, and
\item The next value of $\vec{\theta}$ to try, given the
  $\vec{\theta}$ and $f(\vec{\theta})$ for all previous trials.
\end{enumerate}

We evaluated a total of eight subtly or not so subtly different
learning methods.  All employed a simple random sampling method for
requirement (1); that is, all methods picked their initial
$\vec{\theta}$ value via uniform random sampling within the allowed
parameter ranges. \edit{make sure this is true. Isn't really, should say that we started with A, B, C}.  Thus, the
differences in the algorithms was how they selected new $\vec{\theta}$
values to try from their past experience.

>>>>

For both of these reasons, an intelligent \emph{learning algorithm} is
needed.
In this context, a learning algorithm is a method for choosing
%\begin{enumerate}
%\item The value for $\vec{\theta}$ for the initial trial, and
the next value of $\vec{\theta}$ to try, given a list of the
$\vec{\theta}$ values tried so far and the fitness $f(\vec{\theta})$
measured for each.
%\end{enumerate}

We evaluated a total of seven subtly or not so subtly different
learning methods for the parametrized motion models.  All methods
needed a way of picking a $\vec{\theta}$ for the first trial.  In
general this is done by selecting a random starting vector within the
allowable domain.  However, as discussed in
\secref{fitnessEvaluation}, we decided to evaluate the different
methods starting at one of several common starting points to reduce
one possible contribution of noise.

%All employed a simple random sampling method for
%requirement (1); that is, all methods picked their initial
%$\vec{\theta}$ value via uniform random sampling within the allowed
%parameter ranges. \edit{make sure this is true. Isn't really, should say that we started with A, B, C}.  Thus, the
%differences in the algorithms was how they selected new $\vec{\theta}$
%values to try from their past experience.
